Variational Monte Carlo on bosonic systems

### 2018-04-02 project_1/article/article.tex
Removed unecessary subsection
Figure fix, a bit of discussion writing..

        \subsubsection{Test of Gradient descent}

            Before moving on to the interacting, more interesting systems, it
            would be beneficial to test the gradient descent implementation now
            that we are certain that it moves towards the optimum variational
            parameter $\alpha = \frac{1}{2}$.

@@

\section{Discussion}
    \subsection{Energy per particle}
        For the non-interacting harmonic oscillator system there is no
        difference between a new ``particle'' and new dimensions
        \footnote{This is not entirely true in the case of our implementation of
        the Metropolis algorithms as we draw a single random particle and move
        all dimensions instead of iterating over all particles and all
        dimensions.}. This means that the inclusion of a new particle or
        dimension yields a linear scaling in the energy. Thus if we compute the
        energy per particle for systems of varying size we expect to get the
        same energy. This is most easily seen in \autoref{fig:initial_problem_b}
        and in the expression for the exact energy \autoref{eq:exact_energy}.
        This, however, is \textit{not} the case in the interacting system due to
        the Jastrow factor. Looking at \autoref{tab:10_interacting} and
        \autoref{tab:100_interacting} we see that multiplying the expected
        energy of theformer with $10$ yields a lower number than the latter. We
        can also see this behavior in \autoref{fig:interacting}, where the
        energy per particle for $N = \{10, 50, 100\}$ have been plotted in the
        same figure.

@@

>>>>

@@

\section{Discussion}

	\subsection{Validity of Results}
		The non-interacting tests compared against the analytic "solution" showed
		to a very high degree the validity of the method. One can see this quite clearly 
		from \autoref{fig:initial_problem_b}. Because we get results from simulations
		that correspond to the analytic results we can be fairly certain that the method
		can be expanded upon to include attributes outside the realm problems that are 
		analytically solvable. The systems with elliptic traps and interacting particles are
		such systems.

    \subsection{Energy per particle}
        For the non-interacting harmonic oscillator system there is no
        difference between a new ``particle'' and new dimensions
        \footnote{This is not entirely true in the case of our implementation of
        the Metropolis algorithms as we draw a single random particle and move
        all dimensions instead of iterating over all particles and all
        dimensions.}. This means that the inclusion of a new particle or
        dimension yields a linear scaling in the energy. Thus if we compute the
        energy per particle for systems of varying size we expect to get the
        same energy. This is most easily seen in \autoref{fig:initial_problem_b}
        and in the expression for the exact energy \autoref{eq:exact_energy}.
        This, however, is \textit{not} the case in the interacting system due to
        the Jastrow factor. Looking at \autoref{tab:10_interacting} and
        \autoref{tab:100_interacting} we see that multiplying the expected
        energy of theformer with $10$ yields a lower number than the latter. We
        can also see this behavior in \autoref{fig:interacting}, where the
        energy per particle for $N = \{10, 50, 100\}$ have been plotted in the
        same figure.

@@

\section{Summary Remarks}
